### 2017-01-03 paper/evaluation.tex
added reminder on RQ1
added caption to bash script

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server).

@@

for subj in ${SUBJECTS}; do
    cd ${SUBJECTS_HOME}/${subj}
    mvn clean install -DskipTests ${MAVEN_IGNORES}
    mvn dependency:go-offline
    mvn -o test ${MAVEN_IGNORES} &> ${LOG}
    cat ${LOG} | grep "\[INFO\] Total time:"
done
\end{lstlisting}
\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
    test suites. For each subject, we compile the source and test files, fetch
    all dependencies, and execute the tests in offline mode ignoring
    non-related tasks. Unnecessary commands are omitted for simplicity.}
\end{figure}

@@

To evaluate the presence of parallelization settings, we considered
the \Fix{91} subjects from the groups \emph{long} and \emph{medium}
identified in Section~\ref{sec:rqone}. We focused in these two groups
because they represent costly test suites and are more likely that the
developers may have used strategies to reduce the execution cost (\eg,
running parts of the tests in different threads). We computed the
frequence of the parallelism modes (see Section \ref{sec:modes}) using
a partially manual approach: we first discover automatically the
relevant configuration files and then we manually inspect to eliminate
false-positves (\eg, commented configuration).

@@

In an initial exploration, we searched for
evidences of low-level parallelism settings on configuration files
(\ie, \emph{pom.xml}) from each subject using a semi-automated
approach: we use a script to find all subjects with evidences of
parallel settings and then we manually inspect each configuration file
to eliminate false-positives. In addition, we are interested in
understanding how these parallel settings are used. Given a list of
subjects, our script searches recursively all \emph{pom.xml} files
from the project directory and uses the command-line tool \emph{grep}
to highlight the presence of the keywords \emph{forkMode},
\emph{forkCount}, and \emph{parallel}.  Any of these keywords exist in
any possible combination of parallel settings (see
Section~\ref{sec:modes}). From the 91 subjects, our script detected 43
subjects with evidence of parallel settings. After the inspection of
130 configuration files, we confirmed that \Fix{X} settings are real
parallel configurations.  These settings are related to \Fix{Y}
subjects. It is important to notice that, \Fix{X}\% of the subjects
(\emph{medium} and \emph{long} aggregated) did not explore low-level
parallelism according to our criteria of matching keywords. After the
inspection, this rate raises to \Fix{Y}\%. \Fix{elaborate: some
projects doesn't use parallel features, so what?}
Table~\ref{tab:inspection-table} summarizes our initial findings.

>>>>

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
We executed this experiment \Fix{X} times in our dedicated server
remotely via SSH with the operating system running only essential
services (\eg, the SSH server). \Fix{Describe CPU isolation}

@@

for subj in $SUBJECTS; do
    cd $SUBJECTS_HOME/$subj
    mvn clean install -DskipTests $MAVEN_IGNORES
    mvn dependency:go-offline
    mvn -o test $MAVEN_IGNORES &> $LOG
    cat $LOG | grep "\[INFO\] Total time:"
done
\end{lstlisting}
\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
    test suites. For each subject, we compile the source and test files, fetch
    all dependencies, and execute the tests in offline mode ignoring
    non-related tasks. Unnecessary commands are omitted for simplicity.}
\end{figure}

@@

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqone}. We focused in
these two groups because they represent costly test suites and are
more likely that the developers may have used strategies to reduce the
execution cost (\eg, running parts of the tests in different threads).
We computed the frequence of the parallelism modes (see Section
\ref{sec:modes}) using a semi-automatic approach: we first discover
automatically the relevant configuration files and then we manually
inspect them to eliminate false-positves (\eg, commented
configuration).  Figure \Fix{N} describes the discovery step. We first
list the paths of all build file and then we filter only the build
files that contain any of the keywords, \CodeIn{forkMode},
\CodeIn{forkCount}, or \CodeIn{parallel}. Notice that, for Maven
projects, these any keywords exist in any possible parallelism
configuration \Fix{cite surefire doc}.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
for subj in $SUBJECTS; do
    subject_path="$SUBJECTS_HOME/$subj"
    build_files=`find $subject_path -name pom.xml`
    for build_file in $build_files; do
        output=`cat $build_file | grep "parallel\
                \|forkMode\|forkCount"`
        if [ -z $output ]; then
            echo $build_file
        fi
done
\end{lstlisting}
    \caption{\label{fig:discovery-step} Bash script to filter
    build files (\ie, \emph{pom.xml}) with potentially parallelization
    settings. We first list all build files from a subject (line 3).
    Then, we list the content of the file (\CodeIn{cat} command) and
    redirect the output to filter only the lines that contains any of
    the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
    \CodeIn{forkCount} (\CodeIn{grep} command). If output is not empty
    (line 7), we print the path from the current \emph{pom.xml} file.}
\end{figure}

From the \numSubjsRqTwo{} subjects, there was a total of \Fix{X} build
files and \Fix{Y} to inspect.

@@

From the 91 subjects, our script detected 43 subjects with evidence of
parallel settings. After the inspection of 130 configuration files, we
confirmed that \Fix{X} settings are real parallel configurations.
These settings are related to \Fix{Y} subjects. It is important to
notice that, \Fix{X}\% of the subjects (\emph{medium} and \emph{long}
aggregated) did not explore low-level parallelism according to our
criteria of matching keywords. After the inspection, this rate raises
to \Fix{Y}\%. \Fix{elaborate: some projects doesn't use parallel
features, so what?} Table~\ref{tab:inspection-table} summarizes our
initial findings.
